%-------------------------
% Resume in LaTeX
% Author: Mohammad Aakil Iqbal
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter}
\input{glyphtounicode}

% Page formatting
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS compatibility
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
% Resume Content
%-------------------------------------------

\begin{document}

% Header
\begin{center}
    \textbf{\Huge \scshape Mohammad Aakil Iqbal} \\ \vspace{2pt}
    \small +91-961-606-7913 $|$ \href{mailto:aakiliqbal645@gmail.com}{\underline{aakiliqbal645@gmail.com}} $|$
    \href{https://linkedin.com/in/aakiliqbal}{\underline{linkedin.com/in/aakiliqbal}} $|$
    \href{https://github.com/aakiliqbal}{\underline{github.com/aakiliqbal}}
\end{center}

% Professional Summary
\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Backend Developer with 3+ years of experience building and optimizing high-performance RESTful APIs using Spring Boot and MuleSoft in the financial services domain. AWS Certified Cloud Practitioner with hands-on expertise in Redis caching, asynchronous programming, and AI-assisted development to deliver scalable, production-grade microservices.
    }}
\end{itemize}

% Technical Skills
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, SQL, HTML/CSS \\
     \textbf{Frameworks}: Spring Boot, Spring Security, MuleSoft, Angular, Hibernate/JPA, WebClient \\
     \textbf{Databases}: MySQL, Redis \\
     \textbf{Cloud \& DevOps}: AWS (Certified Cloud Practitioner), Docker, Maven/Gradle, CI/CD \\
     \textbf{Architecture}: REST APIs, Microservices, Multithreading, Asynchronous Programming, API Design \& Development \\
     \textbf{AI Tools \& Automation}: Claude Opus, GPT 5.0, MCP Server, GitHub Integration \\
     \textbf{Tools}: Git, Jira, New Relic, Elasticsearch, ActiveBatch, Postman, Swagger/OpenAPI \\
     \textbf{Certifications}: \href{https://www.credly.com/badges/242089fc-b58e-4362-b319-7de89c0a47af}{\underline{AWS Certified Cloud Practitioner}} \\
    }}
\end{itemize}

% Experience
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Backend Developer}{Mar 2025 -- Present}
      {Fortune 500 Financial Services Client | Wipro}{Gurugram, India}
      \resumeItemListStart
          \resumeItem{Lead architectural decisions and migration of legacy SOAP/MuleSoft APIs to Spring Boot microservices to boost performance and scalability.}
          \resumeItem{Leveraged AI prompting with agents like Claude Opus and GPT 5.0 for code generation, test case writing, and documentation.}
          \resumeItem{Integrated MCP (Model Context Protocol) server with GitHub for automated code reviews, PR analysis, and daily task automation.}
          \resumeItem{Troubleshot critical production issues and managed Jira tickets end-to-end, ensuring system reliability and SLA compliance.}
          \resumeItem{Collaborated with cross-functional teams, vendors, and stakeholders to resolve integration issues swiftly and maintain smooth project delivery.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Backend Developer}{Mar 2023 -- Mar 2025}
      {Fortune 500 Financial Services Client | Wipro}{Gurugram, India}
      \resumeItemListStart
          \resumeItem{Built and enhanced 15+ RESTful APIs using Spring Boot and MuleSoft, migrating legacy SOAP/MuleSoft APIs to Spring Boot microservices.}
          \resumeItem{Introduced Redis caching layer for frequently accessed endpoints, cutting API response times by up to 50\% and reducing database load.}
          \resumeItem{Migrated legacy synchronous RestTemplate to reactive WebClient for non-blocking HTTP calls, improving throughput in high-traffic environments.}
          \resumeItem{Leveraged asynchronous programming and multithreading in Java to enhance API throughput serving 10K+ concurrent users.}
          \resumeItem{Monitored production services with New Relic dashboards and ActiveBatch job scheduling, enabling proactive issue detection and 99.9\% uptime.}
      \resumeItemListEnd
    \resumeSubheading
      {Java Full Stack Developer Intern}{Apr 2022 -- Aug 2022}
      {Wipro}{Remote}
      \resumeItemListStart
          \resumeItem{Developed a full-stack job portal application with Angular for a responsive front-end and Spring Boot REST APIs for robust backend functionality, backed by MySQL.}
          \resumeItem{Implemented advanced search features with pagination and secure JWT-based authentication using Spring Security to enhance user experience and data security.}
          \resumeItem{Wrote unit and integration tests using JUnit and Mockito, achieving 80\%+ code coverage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% Education
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions}{Aug 2018 -- Aug 2022}
      {B.Tech, Electronics and Communication Engineering}{Ghaziabad, India}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Object-Oriented Programming, Database Management Systems, Computer Networks}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% Achievements
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \resumeItemListStart
         \resumeItem{Named \textbf{Top Performer of the Quarter} at Wipro for delivering high-quality results and exceeding client expectations.}
         \resumeItem{Earned the \textbf{Victory League} award for leadership and key contributions to a successful major project release.}
         \resumeItem{Received the \textbf{Habit Flagbearer -- Demonstration Stewardship} award for ensuring timely project delivery and mentoring junior developers.}
     \resumeItemListEnd
    }}
\end{itemize}

\end{document}